\sysfull

### 2018-08-07 paper/asplos19/paging.tex
Paging revised

Resolving WAR (Write-After-Read) dependencies by considering static task boundaries is not sufficient to keep non-volatile memory consistent when task are coalesced. Not handing WAR dependencies with task coalescing introduces a new problem, which we denote as \emph{task coalescing-induced WAR dependency}. This problem is illustrated in Fig.~\ref{figure:coalescedWar}. Therefore, \sys introduces its novel {\em Virtual Memory Manager} (WMM) which enables task coalescing guaranteeing data integrity, which is at the same time efficient.

>>>>

Resolving WAR (Write-After-Read) dependencies by considering static task boundaries is not sufficient to keep non-volatile memory consistent when task are coalesced. Not handing WAR dependencies with task coalescing introduces a new problem, which we denote as \emph{task coalescing-induced WAR dependency}. This problem is illustrated in Fig.~\ref{figure:coalescedWar}. Therefore, \sys implements novel {\em Virtual Memory Manager} (WMM) which enables task coalescing guaranteeing data integrity, which is at the same time efficient.
